\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{leftmargin=1.2em, itemsep=0.15em, topsep=0.15em}

\begin{document}

{\LARGE Chiara Oxender} \hfill Software Engineer\\
\href{mailto:chiara.oxender@gmail.com}{chiara.oxender@gmail.com} \hfill github.com/coxender\\
Lansing, MI \hfill linkedin.com/in/chiara-oxender/


\section*{Core Skills}
\textbf{Languages:} Python, TypeScript, Bash, JavaScript, Java, MSSQL, C\# \\
\textbf{Frameworks:} Django, FastAPI,  Kubernetes, Lit, CDK, CloudFormation\\
\textbf{Tools:} Kafka, SQS, Lambda, StepFunction, IAM, Docker, Jenkins, Codex, GitHub Actions, Argo, Jenkins \\
\textbf{Environments:} AWS, GCP, Linux, Windows\\

\section*{Experience}
\textbf{Auto Owners Insurance} \hfill 2022 -- Present\\
\textit{Senior Data Science Platform Developer}
\begin{itemize}
  \item Architected and developed the first large scale AWS project at the company.
  \item Built and maintained containerized Python machine learning services deployed to Kubernetes clusters.
  \item Reduced security vulnerabilities by 20\% through infrastructure hardening.
 \item Designed a Kubernetes application template that reduced deployment time by multiple days.
 \item Partners with developers and security teams to  create and implement cloud best practices.
 \item Lead division wide workshop series on developer best practices, security, and maintainability.
 \item Designs complex systems for team development. Clarified details, communicated with stakeholders, and developed along with the project team. 
 \item Added testing to several legacy applications, increasing coverage by 40\%.
\end{itemize}

\textbf{Fannie Mae} \hfill 2021 \\
\textit{Technology Management Intern}
\begin{itemize}
  \item Researched internal vulnerabilities by testing AWS services, monitoring logs, and analyzing data.
  \item Viewed and assessed NIST requirements for multiple applications.
\end{itemize}


\section*{Education}
\textbf{Eastern Michigan University} \hfill 2022\\
B.S., Computer Science  | summa cum laude


\section*{Personal Projects}

\textbf{Task Aggregator} TypeScript, Vite\\
 A web app designed to securely track work time.   \\

\textbf{Muninn}  Django, Apache, AWS, MySQL\\
Created a habit tracker website as part of a six person team.  Full stack developer.\\
\end{document}
